### 2015-03-05 fundamentals/acks.tex
Massage the acknoledgements

This work has received institutional support from \gls{ANL}, the \gls{NEUP},
the \gls{NRC}, the \gls{NSF}, and the \gls{UW}.

>>>>

Direct support for the \Cyclus project has been received from the \gls{NRC}
Faculty Development program, the \gls{NEUP} Research \& Development Program,
the \gls{NNSA} Consortium for Verification Technology, and the \gls{UW}.  In
addition students contributing to \Cyclus have received fellowship support
from the \gls{ANL} Lab Grad program, the \gls{NEUP} Fellowship program, the
\gls{NSF} Graduate Fellowship program, and the \gls{DHS} Nuclear Forensics
Graduate Fellowship program.
